Dynamics of Laterally Propagating Flames in X-ray Bursts

### 2019-10-14 xrb/paper.tex
do the appendix

>>>>

To test our implementation of diffusion we created a unit test in
\castro\ that just uses the diffusion solver.  This test uses the
standard Gaussian initial conditions---the diffusion of a Gaussian
remains Gaussian, with a lower amplitude and wider width.  This is run
with a constant diffusion coefficent.  The point of this test is to
demonstrate that the implementation, done in a predictor-corrector
form is second-order accurate.

We use a 2-d axisymmetric geometry, with a reflection boundary on the symmetry axis (left)
and Neumann boundaries on all other sides.  In this geometry, the solution behaves like
a spherical problem, and has the form:
\begin{equation}
  T(r) = T_1 + (T_2 - T_1) \left (\frac{t_0}{t + t_0} \right )^{3/2} e^{-r^2/(4 D (t + t_0))}
\end{equation}
where $t_0$ is a small time used to set the initial width of the
Gaussian, $r$ is the distance from the origin, and $D$ is the
diffusion coefficient.  $T_1$ is the ambient temperature and $T_2$ is
the temperature of the peak of the Gaussian.  We use $D = 1$, $T_1 = 1$, $T_2 = 2$,
and $t_0 = 0.001$.
